### 2022-09-22 main/chapter_context.tex
tweak footnote footnote

\footnotetext{%
This footnote, which was perfected in~\cite{lester2013heffalon},
``should be used in every \atlas\ publication''~\cite{atlas_footnote}.
True to form, internal \atlas\ guidelines ask that
``If you think you can improve on it, please consult with the
Publications Committee''~\cite{atlas_coordinate}.
We added the sentence defining angular distance without such a consultation.%
}

>>>>

\footnotetext{%
This footnote and appears in every \atlas\ publication, and was perfected
in~\cite{lester2013heffalon}.
True to form, internal \atlas\ guidelines ask that
``If you think you can improve on it, please consult with the
Publications Committee''~\cite{atlas_coordinate, atlas_footnote}.
We added the sentence defining angular distance without such a consultation.%
}
